---
title: "Exercise1"
author: "Tiziana Errera"
date: "20/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

_The aim of this exercise is to create a sample of 100 values from a log-normal
distribution (with mu=1 and sigma=.25); then to create the histogram of the distribution and
the distribution on the log scale; and last but not least, to report the mean and variance of the sample in
line in the text._

```{R Sample}
n<-100
Xvalues<-rlnorm(n, meanlog=1, sdlog=0.25)
```

## Histograms

Here there are the histograms of the distributions:

```{r Histograms}
hist(Xvalues)
hist(log10(Xvalues))
```

## Mean and Variance

The mean is:
```{r mean, echo=FALSE}
xmean <- mean(Xvalues)
xmean 
```
While the mean of the log distribution is:
```{r log mean, echo=FALSE}
xlogmean <- mean(log(Xvalues))
xlogmean
```

The variance is:
```{r variance, echo=FALSE}
xvariance <- var(Xvalues)
xvariance
```
While the variance of the log distribution is:
```{r log variance, echo=FALSE}
xlogvariance <- var(log10(Xvalues))
xlogvariance
```
